\section{Description}
\begin{justify}
The project is a web application that helps users compare estimated time and actual time for a task. The main functionality is to accept task details, process them through rule-based analysis, store the result in a database, and return an estimation type with an accuracy value. The project is useful for improving time management and understanding whether a user usually underestimates, overestimates, or accurately estimates work.
\end{justify}

\section{Problem Formulation}
\begin{justify}
Many users plan their tasks based on assumptions rather than previous performance. This creates a gap between expected duration and real completion duration. The project formulates this as a measurable problem: for each task, the expected time and actual time are compared, the absolute difference is calculated, and the estimation category is generated.
\end{justify}

\section{Motivation}
\begin{justify}
Traditional task lists usually record only task names or deadlines. They do not teach the user whether their planning was realistic. Manual comparison is possible but inconvenient and inconsistent. The motivation of this project is to provide a simple digital system that records tasks and gives immediate feedback so that users can improve future estimation habits.
\end{justify}

\section{Proposed Solution}
\begin{justify}
The proposed solution is a full-stack system with a form-based frontend, REST API backend, MySQL storage, and rule-based AI analysis. The system overcomes manual tracking by automatically classifying each task and preserving past task information for dashboard and suggestion features.
\end{justify}

\section{Scope of the Project}
\begin{justify}
The project scope includes task creation, time comparison, rule-based classification, analysis storage, dashboard retrieval, and suggested time based on previous tasks. The current version is intended for academic demonstration and individual productivity tracking. Enterprise scheduling, team collaboration, complex authentication, and machine learning prediction are considered future extensions.
\end{justify}
